\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-24 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
EGU poster: Temporal framework stub
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64901 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Introduction}}
{
Geographical Information Systems (GIS) is known for its capacity 
to spatially enhance the capacity of management of natural resources. 
While being often used as an analytical tool, it also represents a collaborative 
scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
Thus, a large number of scientific geospatial computations depend on quality and 
correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
helps to preserve reproducibility of scientific results over time as the original author 
designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
improvements are tracked in the source code versioning system and are immediately 
available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
generation of scientists.
}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Introduction}}
{
Geographical Information Systems (GIS) are known for their capacity 
to spatially enhance the capacity of management of natural resources. 
While being often used as an analytical tool, they also represent a collaborative 
scientific platform to develop new algorithms. GRASS GIS (Neteler et al., 2012 
\cite{neteler2012grass}), a free and open source GIS, is used by many scientists 
directly or through other projects such as R or QGIS to perform geoprocessing tasks. 
Thus, a large number of scientific geospatial computations depend on quality and 
correct functionality of GRASS GIS. Integrating scientific algorithms into GRASS GIS 
helps to preserve reproducibility of scientific results over time as the original author 
designed it (Rocchini \& Neteler, 2012 \cite{rocchini2012let}). Moreover, subsequent 
improvements are tracked in the source code versioning system and are immediately 
available to the public (Petras, 2014 \cite{Petras2014}). Thus, GRASS GIS acts as a 
repository of scientific peer-reviewed code and algorithm/knowledge hub for future 
generation of scientists.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Temporal framework (TGRASS)}}{

Described some applications

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\column{0.25}
